Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-15 paper/section_5_experiments.tex
Add paragraph on person names

   \item Models which encode articles using GloVe embeddings are unable to
   generate rare proper nouns (precision and recall of 0).
   This is because the encoder skips words that are not part of the fixed GloVe
   vocabulary. Models that use the BPE based article encoder RoBERTa, and thus
   have an unbounded input vocabulary, show
   a clear advantage in rare proper noun generation, with precision as high as
   38.3\% at a recall of 39.9\%.

@@

   \item Adding attention over the faces improves both the recall and precision
   of personal names. It has no significant effect on other entity types (see
   the supplementary materials for a detailed breakdown).

>>>>

   \item Models which encode articles using GloVe embeddings are unable to
   generate rare proper nouns (precision and recall of 0).
   This is because the encoder skips words that are not part of the fixed GloVe
   vocabulary. Models that use the BPE based article encoder RoBERTa, and thus
   have an unbounded vocabulary show
   a clear advantage in rare proper noun generation, with precision as high as
   38.3\% at a recall of 39.9\%.

@@

   \item Adding attention over the faces improves both the recall and precision
   of personal names. It has no significant effect on other entity types (see
   the supplementary materials for a detailed breakdown). Importantly, personal
   names is the most common entity type in news captions and so we also see an
   improvement in BLEU, ROUGE, METEOR, and CIDEr scores. More broadly, this
   result suggests that introducing specialised vision models tuned to the most
   common types of objects such as organisations (via logos or landmarks) is a
   promising way of improving performance on news image captioning.
